%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Compiler Engineer Intern} % Job title
{Wolfram Research} % Organization
{Oxfordshire, UK} % Location
{Jun. 2022 -- Oct. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Joined the small team developing the experimental compiler for Wolfram Language to both CPU and GPU targets.}
\item {Developed an optimization pass for operations on immutable data and added to the Wolfram standard library.}
\item {Drove progress with LLVM, language design, and tooling skills.}
\item {Kept pace with dynamic collaborative work on a complex and evolving code base.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Outreach Ambassador, Tutor, and Teaching} % Job title
{University of Bath, Computer Science Department} % Organization
{Bath, UK} % Location
{Oct. 2019 -- Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Led, authored, and presented \href{https://www.technical-labs.link/notes/2020/}{Technical Labs}; a series of 
  seminars for large groups of undergraduates about software development tools.}
\item {Sessions included: Shell scripting, UNIX based systems, Git, Compilers, Debugging, SSH, Continuous Development, and package managers.}
\item {Tutored labs for Data Structures and Algorithms and Functional Programming modules for the university}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software developer and web developer} % Job title
{Backslash Builds} % Organization
{Bath, UK} % Location
{Jun. 2021 -- Oct. 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked in a small agile team developing web applications for clients.}
\item {Used engineering principles and software design patterns inline with contemporary best practice for software engineering.}
\item {Achieved in systems architecture, code maintenance, and working to specifications.}
\end{cvitems}
}

\end{cventries}
